\newpage

\section{Problem 1 (5 pts)}

\subsection{Answer:}

Assume that p represents the statement "The face of a card is \textbf{blue}" and  q represent "It has a \textbf{prime} on the other side". The proposition could be expressed as p $\rightarrow$ q  \\ \\
We must turn over the card shows the color \textbf{blue}, and expect to see prime. Because this card shows the color blue, to validate the truth of the proposition, this card must be turned over and check if its back has a prime number. In other words, the statement p is true. In order to validate the proposition p $\rightarrow$ q, q has to be true. Therefore the turned card's back is expected to have prime number. \\ \\
Taking the contrapositive of the implication statement, $\neg q $\rightarrow$ \neg p$ ($\neg prime $\rightarrow$ \neg blue$). We must turn over the card shows number \textbf{9} - not a prime number, and expect to not see blue color in the back, in this case, we expect to see yellow. \\ \\
We cannot make any claim based on the card shows number \textbf{11}. In this case, the statement q is true, the card has prime number). The proposition p $\rightarrow$ q will be true regardless the truth value of p - the another side of the card could be blue or yellow. \\ \\
We cannot make any claim based on the card shows \textbf{yellow}. Because the statement p is false in this case ($\neg blue$), as this card has yellow color on one side. Therefore, no matter the back of the card is prime or not prime, this will not affect the truth of the proposition. \\ \\
In conclusion, the cards with visible sides blue and 9 must be turned over.

